\documentclass{article}
\usepackage{hyperref}
\include{macros}
\begin{document}
    \title{Spartan \LLFSM}
    \date{\today}
    \author{Morgan McColl}
    \maketitle
    \tableofcontents
    \newpage
    \section{Introduction}
        The purpose of this paper is to give some documentation of the \textit{Spartan \LLFSM} project. I have originally designed this project to allow users to implement \LLFSMs\/ on the \textit{minispartan6+} evaluation board. The board utilises a \textit{Xilinx Spartan-6 XL25} \FPGA.
    \section{Setup}
        Before you can start building machines in \VHDL, you will need to install a number of dependencies. The following steps are for an ubuntu machine.
        \subsection{\ISE}
            \ISE\/ is the \IDE\/ used for the \textit{Spartan-6} \FPGA.
            \begin{enumerate}
                \item Create a Xilinx account at \href{url}{https://www.xilinx.com/}.
                \item Download and install the Xilinx \ISE\/ webpack found at \href{URL}{\url{https://www.xilinx.com/support/download/index.html/content/xilinx/en/downloadNav/design-tools/v2012_4---14_7.html}}.
                \item Create a license by navigating to \href{URL}{\url{https://www.xilinx.com/member/forms/license-form.html}}
                \item Download and place the license file in \texttt{~/.Xilinx}. Optionally you can run the Xilinx license manager which is installed with \ISE.
            \end{enumerate}
            \subsection{xc3sprog}
                \textit{xc3sprog} is used to transfer the bit file from your computer to the board.
                \exampleBlock{
                    \eitem svn checkout https://svn.code.sf.net/p/xc3sprog/code/trunk xc3sprog-code
                    \eitem cd xc3sprog-code
                    \eitem cmake .
                    \eitem make
                    \eitem make install
                }
                You might also require additional libraries:
                \begin{itemize}
                    \item \textit{libftdi}
                    \exampleBlock{
                        \eitem{sudo apt-get install libftdi1}
                    }
                    \item \textit{libftd2xx} located at \href{URL}{\url{http://www.ftdichip.com/Drivers/D2XX.htm}}.
                \end{itemize}
            \subsection{miniSProg (optional)}
                This program provides a \GUI\/ for xc3sprog. It requires qt4/5 and \textit{qtcreator} to install.
                \exampleBlock{
                    \eitem{sudo apt-get install build-essential}
                    \eitem{sudo apt-get install qtcreator}
                    \eitem{sudo apt-get install qt5-default}
                    \eitem{git clone https://github.com/scarabhardware/miniSProg}
                    \item[] Open the project using \textit{qtcreator} (the project file is located at \texttt{./miniSProg/miniSProg/miniSProg.pro}).
                    \item[] Build the project.
                }
            \subsection{Haskell}
                You also need \ghc.
                \exampleBlock{
                    \eitem{sudo apt-get install haskell-platform}
                }
            \subsection{Additional \MiPal\/ Software}
                You will need an \IDE\/ to create the machine format (MiCase, MiPalCase, MiEdit (not tested)).
            \subsection{Installing Spartan \LLFSM}
                \begin{enumerate}
                    \item Navigate to the interpretor folder in the root directory of this repository.
                    \exampleBlock{
                        \eitem{make}
                        \eitem{make install}
                    }
                    \item This command will create a binary called spartanllfsm in \texttt{/usr/local/bin}
                \end{enumerate}
        \section{Methodology}
            We will now examine the process of creating \LLFSMs\/ for implementation on \FPGAs. The process is summarised by the following steps.
            \begin{enumerate}
                \item The user designs their machine in a \GUI\/ using \VHDL.
                \item The user uses the \textit{spartanllfsm} binary to generate a single \VHDL\/ source file.
                \item The user integrates this source file into an existing \ISE\/ project.
            \end{enumerate}
            We will go through this process by following an example of using a \DIP\/ switch to toggle an \LED\/ on or off.
            \subsection{Creating the Machine}
                I have created the machine called \textit{LightToggle.machine} in the machines folder of this repository. The machine contains three states: \textsf{Compare}, \textsf{On} and \textsf{Off} where the \textsf{Compare} state is the initial state. The machine has two external variables: \textit{leds} and \textit{dip}. You will notice that the external variables are declared with a type of \textit{\#extern}. This is a macro interpreted by the code generated to distinguish external variables. A similar type \textit{\#machine} is used to distinguish machine variables. The \textit{\#extern} macro is required on external variables to place them in the appropriate location in the \VHDL\/ source file. The machine simply turns the \LEDs\/ on or off depending on the state of the \DIP\/ switch.
            \subsection{Creating the ISE Project}
            \subsection{Integrating the Machine Source File into the ISE Project}
\end{document}